### 2021-03-03 paper.Rmd
mapped out places for plots

A tour can be considered to be a dynamic graphic, because it shows a smooth sequence of projections over time, ideally with controls that allow stopping, reversing, changing direction, or going forward again. It can be useful to embed a tour into an interactive graphics system, where plots can be queried and elements highlighted (see for e.g. @Swayne2003-cc or @Tierney1991). To create the smooth sequence, a geodesic interpolation is computed between consecutive frames.  It allows the viewer to extrapolate from the low-dimensional to  shapes corresponding to multivariate distribution, and is particularly useful for detecting clusters, outliers and non-linear dependence. 
While tours are invaluable for assessing the geometry of data, they are by no means the only technique available for visualising structure in high dimensional data. An early technique proposed for assessing pairwise relationships between variables is the scatter plot matrix (SPLOM) [@Tukey1983-fj] <!-- there might be others here(?) -->. In this graphic, the canvas is split into a matrix where each off-diagonal element is a scatter plot of variable pairs, while the diagonal elements are either left blank or represent univariate structure. The SPLOM allows the viewer to assess correlation structure but does not scale to large numbers of variables.

@@

@@

@@

- Geodesic interpolation (Ursula)
- Slices vs projections (Ursula)
- Transformations on projections (Ursula)

@@

- Stop/start/reverse
- Manual (Nick)
- Linked brushing (Earo)
- Spin-and-brush  (Ursula)

@@

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)
- Physics (Ursula)
- Bioinformatics (Stuart)

@@

@@

>>>>

A tour can be considered to be a dynamic graphic, because it shows a smooth sequence of projections over time, ideally with controls that allow stopping, reversing, changing direction, or going forward again. It can be useful to embed a tour into an interactive graphics system, where plots can be queried and elements highlighted (see for e.g. @Swayne2003-cc or @Tierney1991). To create the smooth sequence, a geodesic interpolation is computed between consecutive frames.  It allows the viewer to extrapolate from the low-dimensional to  shapes corresponding to multivariate distribution, and is particularly useful for detecting clusters, outliers and non-linear dependence.

> figure 1 illustrating tour views vs nonlinear dimension reduction for Stuart's cluster example

While tours are invaluable for assessing the geometry of data, they are by no means the only technique available for visualising structure in high dimensional data. An early technique proposed for assessing pairwise relationships between variables is the scatter plot matrix (SPLOM) [@Tukey1983-fj] <!-- there might be others here(?) -->. In this graphic, the canvas is split into a matrix where each off-diagonal element is a scatter plot of variable pairs, while the diagonal elements are either left blank or represent univariate structure. The SPLOM allows the viewer to assess correlation structure but does not scale to large numbers of variables.

@@

> figure 2 diagram illustrating a projection

@@

> figure 3 diagram illustrating different displays for different d

@@

> figure 4 diagram illustrating different types of target generation

- Geodesic interpolation (Ursula)

> figure 5 diagram illustrating geodesic interpolation

- Slices vs projections (Ursula)

> figure 6 diagram illustrating projection vs slice

- Transformations on projections (Ursula)

> figure 7 diagram of burning sage transformation

@@

- Stop/start/reverse

> pull something from ggobi book?
> figure 8 illustration

- Manual (Nick)

> something from nick's paper
> figure 9 illustration

- Linked brushing (Earo)

> something from ggobi book
> > figure 10: plots showing example

- Spin-and-brush  (Ursula)

> something from ggobi book
> figure 11: plots showing example

@@

- Model vis examples eg random forest (from Hadley, removing the blindfold) (Natalia)

> figure 12 tour plot(s) of vote matrix and tour plot(s) of variables, with some annotation of cases?

- Physics (Ursula)

> figure 13

- Bioinformatics (Stuart)

@@

> figure 14

@@

> figure 15

- neural networks (from Scheidegger - Stuart)

> figure 16
